Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-06-21 GWLDCII.tex
rewrote remark 3.10

Suppose we are going through the algorithm to construct $I_i^W$ for some $i$, and we are currently at step $j$ of the loop.  Consider the diagram $W'$ formed by $W$ with all the propagators already contributed removed; think of a vertex being taken away when it is contributed, since it can only contribute once, so it is gone from the point of view of the rest of the construction of $I_i^W$.  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.  Again let $V'$ be $V$ with all the propagators already contributed removed.

>>>>

Suppose we are going through the algorithm to construct $I_i^W$ for some $i$, and we are currently at step $j$ of the loop.  Consider the diagram $W'$ formed by $W$ with all the propagators already contributed removed. Not that the algorithm automatically removes a propagator once it contibutes to the algorithm.  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.  Again let $V'$ be $V$ with all the propagators already contributed removed. \sanote{rewrote, correct?}
